---
title: "Quantitative Text Analysis in R"
subtitle: "A gentle hands-on introduction"
output: 
  xaringan::moon_reader:
    css:
      - default
      - css/styles.css
      - css/fonts.css
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%<br>"
      ratio: "16:9"
    includes:
      after_body: "collapseoutput.js"
---


layout: true

<style>
.onehundredtwenty {
  font-size: 120%;
   }

<style>
.ninety {
  font-size: 90%;
   }

.eightyfive {
  font-size: 85%;
   }
   
.eighty {
  font-size: 80%;
   }
   
.seventyfive {
  font-size: 75%;
   }
   
.seventy {
  font-size: 70%;
   }
   
.fifty {
  font-size: 50%;
   }
   
.forty {
  font-size: 40%;
   }
</style>


```{r meta, echo=FALSE, warning=F, message=F}


library(metathis)
meta() %>%
  meta_general(
    description = "Quantitative Text Analysis in R",
    generator = "xaringan and remark.js"
  ) %>%
  meta_name("github-repo" = "favstats/xxx") %>%
  meta_social(
    title = "Quantitative Text Analysis in R",
    url = "https://www.favstats.eu",
    og_type = "website",
    og_author = "Fabio Votta",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@favstats"
  )
```



```{r setup, include=FALSE}
# dateWritten <- format(as.Date('2020-05-04'), format="%B %d %Y")
workshop_day <- format(as.Date("2022-06-29"), format="%B %d %Y")
pacman::p_load(tidyverse, fontawesome, tidyverse, knitr, xaringanthemer)

options(
    htmltools.dir.version = FALSE,
    knitr.table.format = "html",
    knitr.kable.NA = ""
)
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3 # Better figure resolution
)



# Enables the ability to show all slides in a tile overview by pressing "o"
xaringanExtra::use_tile_view()
xaringanExtra::use_panelset()
xaringanExtra::use_clipboard()
# xaringanExtra::use_share_again()
# xaringanExtra::style_share_again(share_buttons = "all")
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,
  mute_unhighlighted_code = FALSE
)
# xaringanExtra::use_webcam()


knitr::opts_chunk$set(warning = F, message = F) # Whether to display errors
```



---
name: title-slide
class: title-slide, center, middle


<div class="my-logo-right"></div> 

<br>

# .font150[.fancy[`r rmarkdown::metadata$title`]] 

### .font120[.fancy[`r rmarkdown::metadata$subtitle`]]

*Spring Camp University of Warwick*

Instructor: Fabio Votta

[`r fa(name = "twitter", fill = "white")` @favstats](http://twitter.com/favstats)<br>
[`r fa(name = "github", fill = "white")` @favstats](http://github.com/favstats)<br>
[`r fa(name = "globe", fill = "white")` favstats.eu](https://www.favstats.eu)


29th June 2022 (Day 2)

.fifty[Link to slides: [favstats.github.io/WarwickSpringCamp_QTA/slides/day2/](https://favstats.github.io/WarwickSpringCamp_QTA/slides/day2/)]

---


## Part-of-speech tagging

---

## Topic Models

---

## Supervised machine learning

